Localization properties, observable character and computational reliability of the linear response in open systems

### 2018-06-07 AnalyticStructure_main.tex
update

\appendix
\section{Eigenvalue equations of the Liouvillian superoperator}

Derive the equations of motion for the excited states. Discussion of the effects of various supplementary conditions...

>>>>

\appendix
\section{Left and right action of the Liouvillian superoperator}

% The Liouvillian superoperator for self-consistent systems is expressed as the sum of the unperturbed part plus a coupling term due the density dependence of the ground-state Hamiltonian.
% Its left action reads
% \begin{align}\lb{LiouvillianLeftActionDef1}
% \Liouv\op O &= \commutator{\hnot}{O} + \commutator{\op V'[\op O]}{\dmnot}  = \nn \\
% &=  \commutator{\hnot}{O} + \op Q_0\op V'[\op O]\dmnot - \dmnot\op V'[\op O]\op Q_0 \;
% \end{align}
% thanks to the equivalence $\commutator{\dmnot}{\op O} = \dmnot \op O \op Q_0 - \op Q_0 \op O \dmnot$. 
% It is also useful to define the scalar coupling kernel $U$
% \be
% U\left[\op O; \op O'\right] \equiv  \int \dd \r \dd \r' \trace{\op O \frac{\delta \hnot }{\delta \rho_0(\r,\r')}
% } \trace{\op O' \ket{\r} \bra{\r'}} \;, \nn
% \ee
% that allows us to express $\op V'[\op O]$ as:
% \be\lb{VpDef1}
% \op V'[\op O]= 
% \int \dd \r \dd \r' U\left[\ketbra{\r}{\r'};\op O\right] \ketbra{\r'}{\r}\;.
% \ee
% The right action of $\Liouv$ can be assessed through the equivalence $\trace{\op O'(\Liouv\op O)} = \trace{(\op O'\Liouv)\op O}$ and provides:
% \be
% \op O\Liouv = -\commutator{\hnot}{\op O} + \int \dd\r\dd\r'
% U\left[\commutator{\dmnot}{\op O};\ketbra{\r'}{\r}\right]\ketbra{\r}{\r'} \;. \nn
% \ee
% Using the symmetry of the coupling kernel we have
% \begin{align}%\lb{LiouvillianRightActionDef1}
% \op O\Liouv &= -\commutator{\hnot}{\op O} + \nn \\ 
% &+ \dmnot\op V'\left[\commutator{{\dmnot}}{\op O}\right]\op Q_0 + \op Q_0\op V'\left[\commutator{\dmnot}{\op O}\right]\dmnot 
% \end{align}

The Liouvillian superoperator $\Liouv$ for self-consistent systems is expressed as the sum of the unperturbed part plus a coupling term due
the density dependence of the ground-state Hamiltonian. The left action of these terms reads, respectively
\be\lb{LiouZeroDef1}
\Liouvnot \op O = \commutator{\hnot}{O} \;,
\ee
and
\be\lb{CouplDef1}
\coupl\op O = \commutator{\op V'[\op O]}{\dmnot}  = \op Q_0\op V'[\op O]\dmnot - \dmnot\op V'[\op O]\op Q_0 \;.
\ee
Here $\op V'$ can be conveniently expressed by defining the \emph{scalar coupling kernel}
\be
U\left[\op O; \op O'\right] \equiv  \int \dd \r \dd \r' \trace{\op O \frac{\delta \hnot }{\delta \rho_0(\r,\r')}
} \trace{\op O' \ket{\r} \bra{\r'}} \;, \nn
\ee
on the basis of which
\be\lb{VpDef1}
\op V'[\op O]= 
\int \dd \r \dd \r' U\left[\ketbra{\r}{\r'};\op O\right] \ketbra{\r'}{\r}\;.
\ee
In view of building the spectral decomposition we are interested in finding both the left and right eigenstates of $\Liouv$.   
The right action of $\Liouv$ can be assessed through the equivalence $\trace{\op O'(\Liouv\op O)} = \trace{(\op O'\Liouv)\op O}$, so that:
\be
\op O\Liouv = -\commutator{\hnot}{\op O} + \int \dd\r\dd\r'
U\left[\commutator{\dmnot}{\op O};\ketbra{\r'}{\r}\right]\ketbra{\r}{\r'} \;. \nn
\ee
In the cases relevant for the present analysis the coupling kernel is symmetric with respect to the exchange of its arguments so
\begin{align}\lb{LiouvillianRightActionDef1}
\op O\Liouv &= -\commutator{\hnot}{\op O} + V'\left[\commutator{{\dmnot}}{\op O}\right] = -\commutator{\hnot}{\op O} + \nn \\ 
&+ \dmnot\op V'\left[\commutator{{\dmnot}}{\op O}\right]\op Q_0 + \op Q_0\op V'\left[\commutator{\dmnot}{\op O}\right]\dmnot \;, 
\end{align}
where in the last equivalence we have made usage of the transverse property of the coupling superoperator. Formula \eqref{LiouZeroDef1},\eqref{CouplDef1}
and \eqref{LiouvillianRightActionDef1} are the starting point for the solution of the eigenvalues equations \eqref{ExcitationOperatorsDef1}.
